Simulation Plots

### 2015-03-24 Simulation/SpectraVisualization.Rmd
change parameters values

```{r, echo=FALSE}

inputPanel(
  sliderInput("v_galaxy", label = "Galaxy Velocity:",
              min = 1, max = 4, value = 1, step = 1),

  sliderInput("v_outflow", label = "Outflow Velocity:",
              min = 100, max = 500, value = 100, step = 100),

@@

  v_galaxy_options <- c(0, 20, 100, 200)

@@

  vg <- v_galaxy_options[input$v_galaxy]
  vo <- input$v_outflow
  lnh <- lognh_options[input$lognh_outflow]

@@

  ggplot(spectrum_sub, aes(x=x,y=y)) + geom_line(col = 30, lw = 2) + labs(title=text, x="Lambda (A)", y="Intensity (Arbitrary Units)") + xlim(1210, 1232) + ylim(0, 7100) + theme(plot.title = element_text(hjust = 1, vjust = 1))

>>>>

```{r, echo=FALSE}
library(shiny)

inputPanel(
  selectInput("v_galaxy", label = "Galaxy Velocity:", 
              choices = c("60 km/s" = 60, "125 km/s" = 125), ),

  selectInput("v_outflow", label = "Outflow Velocity:", 
              choices = c("100 km/s" = 100, "200 km/s" = 200), ),

@@

@@

  vg <- input$v_galaxy
  vo <- input$v_outflow
  lnh <- lognh_options[input$lognh_outflow]

@@

  ggplot(spectrum_sub, aes(x=x,y=y)) + geom_line(col = 30, lw = 2) + labs(title=text, x="Velocity (km/s)", y="Intensity (Arbitrary Units)") + xlim(-1000, 4010) + ylim(0, 6500) + theme(plot.title = element_text(hjust = 1, vjust = 1))
